\documentclass{article} % For LaTeX2e
\usepackage{iclr2020_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}


\title{Which spherical CNN should you use?\\ DeepSphere V2}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review. 
\author{Michaël Defferrard, Martino Milani, Frédérick Gusset,  Nathanaël Perraudin \thanks{ Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

\begin{abstract}
story / main point:

* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\

contributions:\\
* theory => convergence (better graph)\\
* experiments on relevant problems (not spherical MNIST) => check the desiderata\\
  * surprising: anisotropy doesn't seem useful\\

\end{abstract}

\section{Introduction [2 pages]}
Get inspiration from DeepSphere V1\\

Why are spherical CNNs important? What are the application?\\
See DeepSphere workshop paper\\

Desiderata:\\
* respect the domain\\
  * rotational equivariance\\
  * deformation (e.g., on the icosahedron for gauge)\\
* powerful / generality => isotropic vs anisotropic\\
* scale: computational cost \& memory usage (feature maps)\\
* flexible (samplings, irregular), simplicity (implementation)\\

\begin{table}[h!]
    \centering
    \begin{tabular}{l|c|c|c|c}
         & Scale & Generality& equivariance & Flexibility \\
         \hline
        Cohen & & & &  \\
         \hline
        Gauge & & & &  \\
         \hline
        Esteves & & & &  \\
         \hline
        Jiang & & & &  \\
         \hline
        2D CNN (cubed sphere) & & & &  \\
         \hline
        Ours & & & &  \\
    \end{tabular}
    \caption{Caption}
    \label{tab:my_label}
\end{table}

On the one side, we have Cohen which is computationally very expensive but perfectly equivariant, on the other we have cube sphere which computationl very good but not equivariant at all. Other methods are tradedoff between these two. What is a good tradeoff? We think that DeepSphere is

Present the different spherical CNNs with pro and cons => mostly scale vs generality\\
* 2D CNN => doesn't respect geometry and equivariance\\
* Cohen spherical CNN => most general, but doesn't scale\\
* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)\\
* Esteves => ?
* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)\\

\section{Method [1 pages]}

* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere}
* equiangular: Renata \& Pascal

\section{Rotation equivariance [2.5 pages]}

\subsection{Link with the Laplace-Beltrami Operator}

\subsection{Convergence theorem}

\subsection{Equivariance error}

* define a measure of equiv error\\
* show convergence empirically\\
* improved upon V1\\
* no difference in practice (see experiment xx) => NNs are resilient to equiv error\\

\section{Experiments [2 pages]}
Which experience show that DeepSphere V1 and V2 are equivalent in practice.

\subsection{3D object recognition}

* same perf as other spherical CNNs, but 40 times faster
* compare the two samplings => not much difference

\subsection{cosmo}

other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most)

\subsection{Climate event detection}

* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed\\
* cannot compare with Mudigonda (16 vs 1 input channel)\\
* full: we scale (50B pixels, 20TB) => lead to better perf?\\

\subsection{GHCN}

* task is artificial, but it shows DeepSphere's flexibility\\
* structure (looking around) help for prediction\\

\section{Conclusion [0.5 pages]}

* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.\\
  * respect geometry: No need for a very precise equivariance, i.e. a very good graph...\\
  * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
  * scales linearly => cannot do better ($n^1.25$ for best HEALPix, linear for not optimal)\\
  * flexible => independent of the sampling\\

future work:\\
* when anisotropy useful? (research question)\\
* irregular sampling while respecting the geometry\\
* beyond the sphere, any manifold\\




\newpage

\subsubsection*{Author Contributions}
If you'd like to, you may include  a section for author contributions as is done
in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Use unnumbered third level headings for the acknowledgments. All
acknowledgments, including those to funding agencies, go at the end of the paper.


\bibliography{references}
\bibliographystyle{iclr2020_conference}

\newpage

{\LARGE \sc {Title of the paper: Supplementary Material}}
\appendix
\section{Proof of theorem}


\section{Experiments details}




\end{document}
